Stable quantum memories with limited measurement

### 2017-06-06 IsingECC/manuscript_ising_ecc_final.tex
updated figure caption

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects on a unit cell.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.}
\label{fig:detect_swap}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\scalebox{1}{\includegraphics[width=1.0\columnwidth]{detect_swap.pdf}}
\end{center}
\caption{This cartoon illustrates the ``centering'' procedure for detected defects on a unit cell.  Spin variables are in gray, and domain wall variables are in blue (no defect present) and red (defect present).  When a defect is detected on a measurement patch (blue box), it is swapped to the center of the measurement patch via the $\rm{DSWAP}$ operator (black arrows).  The defect immediately adjacent to it is also swapped onto the measurement patch so as not to pull apart defect pairs that would have otherwise dissipated.  Measurement patch lengthscale $\lambda$ indicated by arrow on top, and unit cell lengthscale $\lambda$ indicated by arrow on bottom.}
\label{fig:detect_swap}
\end{figure}
